---
title: "renv"
author: "Sean Wilson"
date: "4/23/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Reproducible Environments

This rmd file is based off a post at <https://www.r-bloggers.com/reproducible-environments/>

## Premise

An environment consists of all the dependencies required to enable your code to
run correctly. This includes R itself, R packages, and system dependencies. As
with many programming languages, it can be challenging to manage reproducible R
environments.

A strategy for safely upgrading packages consists of three steps:

Isolate a project
Record the current dependencies
Upgrade packages

## using renv

The first step in this strategy ensures one project’s packages and upgrades
won’t interfere with any other projects. Isolating projects is accomplished by
creating per-project libraries. A tool that makes this easy is the new <https://github.com/rstudio/renv> renv
package. Inside of your R project, simply use:

```{r}
devtools::install_github("rstudio/renv")
```


```{r}
# inside the project directory
renv::init()
```

The second step is to record the current dependencies. This step is critical
because it creates a safety net. If the package upgrade goes poorly, you’ll be
able to revert the changes and return to the record of the working state. Again,
the renv package makes this process easy.

```{r}
# record the current dependencies in a file called renv.lock
renv::snapshot()

# commit the lockfile alongside your code in version control
# and use this function to view the history of your lockfile
renv::history()

# if an upgrade goes astray, revert the lockfile
renv::revert(commit = "abc123")

# and restore the previous environment
renv::restore()
```

With an isolated project and a safety net in place, you can now proceed to
upgrade or add new packages, while remaining certain the current functional
environment is still reproducible. The pak <https://github.com/r-lib/pak>
package can be used to install and upgrade
packages in an interactive environment:

```{r}
devtools::install_github("r-lib/pak")

# upgrade packages quickly and safely
pak::pkg_install("ggplot2")
```


```{r}
renv::snapshot(lockfile = "efg")

pak::pkg_install("broom")

renv::history()
renv::restore(lockfile = "abc")


```

















